---
pagetitle: Rmd report
output:
  html_document:
    highlight: zenburn
    theme: cosmo
    df_print: paged
    toc: yes
    code_folding: hide
    code_download: true
---

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,

  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## make all required libraries available by loading radiant package if needed
if (is.null(shiny::getDefaultReactiveDomain())) library(radiant)
```

<style>
.btn, .form-control, pre, code, pre code {
  border-radius: 4px;
}
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
code, pre, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
}
code {
  color: #c7254e;
  background-color: #f9f2f4;
}
pre {
  background-color: #ffffff;
}
</style>

## RFM for Bookbinders

Start by loading the `bbb.rds` data into Radiant using the _Data > Manage_ tab. Then press the report icon <i title='Report results' class='fa fa-edit'></i> icon on the bottom-left of the screen to add the relevant R-code to _Report > Rmd_.

```{r}
## load the original tibble from data/bbb.rds
bbb_file <- tempfile()
curl::curl_download(
  "https://www.dropbox.com/s/i6athvk5m4t822m/bbb.rds?dl=1",
  destfile = bbb_file
)
bbb <- readr::read_rds(bbb_file)
```

### Assessing recency

Create a bar-plot using `buyer` as the Y-variable and `last` as the X-variable.

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "last",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'", 
    x = "months since last purchase (last)"
  ),
  custom = FALSE
)
```

Plot a histogram of the `last` variable (set plot type to "distribution") 

```{r fig.width = 6.46, fig.height = 4.31, dpi = 288}
visualize(bbb, xvar = "last", type = "dist", custom = FALSE)
```

Create the `recency` variable `rec_iq` using the following command in _Data > Transform > Create_:

`rec_iq = xtile(last, 5)`

```{r}
## create recency quintiles
bbb <- mutate(bbb, rec_iq = xtile(last, 5))
```

Is recency predictive of purchase? Are the best customers in quintile 1? The graph below shows this is indeed the case.

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "rec_iq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'", 
    x = "Recency quintiles (rec_iq)"
  ),
  custom = FALSE
)
```

### Assessing frequency

The plot below shows that purchase probability is NOT highest in the 1st quantile for frequency (`purch`).

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "purch",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'",
    x = "Purchase frequency (purch)"
  ),
  custom = FALSE
) 
```

This means we need to _flip_ the bin numbers so the highest purchase probability will bin in the 1st bin (quantile). The easiest way to do this is to add `rev = TRUE` in the call to `xtile`.

`freq_iq = xtile(purch, 5, rev = TRUE)`

Alternatively, you could use:

`freq_iq = 6L - xtile(purch, 5)`

```{r}
## create frequency quintiles
bbb <- mutate(bbb, freq_iq = xtile(purch, 5, rev = TRUE))
```

Is frequency predictive of purchase? Are the best customers in quintile 1? The graph below shows this is now indeed the case.

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "freq_iq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'", 
    x = "Frequency quintiles (freq_iq)"
  ),
  custom = FALSE
)
```

Why are there only 4 values? Looking at the histogram below we see that the distribution of `purch` is heavily skewed (to the right). This makes it difficult for the binning algorithm to create 5 _bins_ of similar size

```{r fig.width = 7, fig.height = 4.67}
visualize(bbb, xvar = "purch", color = "freq_iq")
```

### Assessing monetary value

The plot shows that purchase probability will NOT be highest in the 1st monetary quantile (`total`)

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "total",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'", 
    x = "Monetary value (total)"
  ), 
  custom = TRUE
) + 
  theme(
    axis.ticks.x = element_blank(), 
    axis.text.x = element_blank()
  )
```

Plot a histogram of the `total` variable

```{r fig.width = 6.46, fig.height = 4.31, dpi = 288}
visualize(bbb, xvar = "total", type = "dist", custom = FALSE)
```

Just like we did for `frequency`, we have to _flip_ the bins so the highest purchase probability is in the 1st quantile. The easiest way to do this is to add `rev = TRUE` in the call to `xtile`. 

`mon_iq = xtile(total, 5, rev = TRUE)`

```{r}
## create monetary quintiles
bbb <- mutate(bbb, mon_iq = xtile(total, 5, rev = TRUE))
```

Is monetary predictive of purchase? Are the best customers in quintile 1? The graph below shows this is now indeed the case.

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "mon_iq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'", 
    x = "Monetary value quantiles (mon_iq)"
  ),
  custom = FALSE
)
```

## Correlation between RFM variables

What is the correlation between `last`, `total`, and `purch`?

```{r fig.width = 6.73, fig.height = 6.73}
result <- correlation(bbb, vars = c("last", "total", "purch"))
summary(result)
plot(result, n = 1000)
```

Create a new variable that captures the average amount spent per purchase (`avg_total`).

```{r}
## calculate average spend
bbb <- mutate(bbb, avg_total = total / purch)
```

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "purch",
  yvar = "avg_total",
  type = "bar",
  custom = FALSE
)
```

What is the correlation between `purch` and `avg_total`?

```{r fig.width = 7.54, fig.height = 7.54}
result <- correlation(
  bbb,
  vars = c("last", "total", "purch", "avg_total")
)
summary(result)
plot(result, n = 1000)
```

## Generate RFM index

Use _Data > Transform > Create_ to generate the RFM index by _pasting_ `rec_iq`, `freq_iq`, and `mon_iq` together. 

`rfm_iq = paste0(rec_iq, freq_iq, mon_iq)`

```{r}
## create new variable(s)
bbb <- mutate(bbb, rfm_iq = paste0(rec_iq, freq_iq, mon_iq))
```

```{r fig.width = 10.5, fig.height = 4.67}
visualize(
  bbb,
  xvar = "rfm_iq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyer = 'yes'", 
    x = "Independent RFM index (rfm_iq)"
  ),
  custom = TRUE
) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Generate sequential quintiles

There is no need to do anything with `recency` for a sequential quintiles approach because `rec_iq` is the same as `rec_sq`. However, to calculate `freq_sq` we first need to group the data by `rec_iq` before applying the `xtile` function. Subsequently, we need to group the data by `rec_iq` and `freq_sq` before applying the `xtile` function to calculate `mon_sq` 

```{r}
## calculate sequential frequency quintiles
bbb <- group_by(bbb, rec_iq) %>%
  mutate(freq_sq = xtile(purch, 5, rev = TRUE)) %>%
  ungroup()

## calculate sequential monetary quintiles
bbb <- group_by(bbb, rec_iq, freq_sq) %>%
  mutate(mon_sq = xtile(total, 5, rev = TRUE)) %>%
  ungroup()
```

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "freq_sq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'", 
    x = "Frequency quintiles (freq_sq)"
  ),
  custom = FALSE
)
```

```{r fig.width = 7, fig.height = 4.67}
visualize(
  bbb,
  xvar = "mon_sq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyers = 'yes'", 
    x = "Monetary value quintiles (mon_sq)"
  ),
  custom = FALSE
)
```

## Generate Sequential RFM index

Use _Data > Transform > Create_ to generate the RFM index by _pasting_ `rec_iq`, `freq_sq`, and `mon_sq` together. 

`rfm_sq = paste0(rec_iq, freq_sq, mon_sq)`

```{r}
## create new variable(s)
bbb <- mutate(bbb, rfm_sq = paste0(rec_iq, freq_sq, mon_sq))
```

```{r fig.width = 10.5, fig.height = 4.67}
visualize(
  bbb,
  xvar = "rfm_sq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyer = 'yes'", 
    x = "Sequential RFM index (rfm_sq)"
  ), 
  custom = TRUE
) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Calculate performance metrics without targeting

## Response rate without RFM

We can use _Data > Explore_ to generate summary statistics for the `buyer` variable in the sample

```{r}
result <- explore(
  bbb,
  vars = "buyer",
  fun = c("n_obs", "mean")
)
summary(result, dec = 4)
```

Some basic R-code is needed to to calculate performance metrics for BBB when no targeting is used. We are now using R as a calculator.

```{r}
perc_mail <- 1
nr_mail <- 500000 * perc_mail
rep_rate <- mean(bbb$buyer == "yes")
nr_resp <- nr_mail * rep_rate
mail_cost <- .5 * nr_mail
profit_nt <- (18 - 9 - 3) * nr_resp - mail_cost
ROME_nt <- profit_nt / mail_cost
```

Without targeting BBB would mail all `r format_nr(nr_mail, dec = 0)` remaining customers (`r format_nr(perc_mail, perc = TRUE)`). The response rate is predicted to be `r format_nr(rep_rate, perc = TRUE)` or `r format_nr(nr_resp, dec = 0)` buyers. The expected profit is `r format_nr(profit_nt,"$", dec = 0)`. The mailing cost is estimated to be `r format_nr(mail_cost, "$", dec = 0)` with a ROME of `r format_nr(ROME_nt, perc = TRUE)`

## Calculate performance metrics using independent RFM

## Break-even (aggr)

We can calcule the break-even response rate as follows:

`.5 / (18 - 9 - 3) = `r (breakeven = .5 / (18 - 9 - 3))``

The breakeven value is `r format_nr(breakeven, dec = 1, perc = TRUE)`.  All cells above the breakeven line in the plot below should be mailed.

```{r fig.width = 10.5, fig.height = 4.67}
visualize(
  bbb,
  xvar = "rfm_iq",
  yvar = "buyer",
  type = "bar",
  labs = list(
    y = "Proportion of buyer = 'yes'", 
    x = "Independent RFM index (rfm_iq)"
  ),
  custom = TRUE
) +
  geom_hline(yintercept = 0.083) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Response rate using independent quintiles

Create the `mailto_iq` variable for independent RFM making sure to select the `rfm_iq` variable so the estimates are generated for each cell.

`mailto_iq = mean(buyer == "yes") > .083`

```{r}
## mail TRUE or FALSE
bbb <- group_by(bbb, rfm_iq) %>%
  mutate(mailto_iq = mean(buyer == "yes") > breakeven) %>%
  ungroup()

## also calculate response rate per group as an illustration
bbb <- group_by(bbb, rfm_iq) %>%
  mutate(rfm_iq_resp = mean(buyer == "yes")) %>%
  ungroup()
```

```{r}
result <- pivotr(
  bbb,
  cvars = "mailto_iq",
  fun = "n_obs",
  normalize = "total"
)
summary(result, dec = 2, perc = TRUE)
```

```{r}
result <- explore(
  bbb,
  vars = "buyer",
  byvar = "mailto_iq",
  fun = c("n_obs", "mean")
)
summary(result, dec = 4)
```

## Calculate profits and ROME for Independent RFM

Some basic R-code is again needed to to calculate performance metrics for BBB when targeting using independent RFM. The only difference with the calculations above is that we now also have calculate the percentage of customers that will be mailed rather than setting equal to 100%.

```{r}
perc_mail <- mean(bbb$mailto_iq)
nr_mail <- 500000 * perc_mail
dat <- filter(bbb, mailto_iq == TRUE)
rep_rate <- mean(dat$buyer == "yes")
nr_resp <- nr_mail * rep_rate
mail_cost <- .5 * nr_mail
profit_iq <- (18 - 9 - 3) * nr_resp - mail_cost
ROME_iq <- profit_iq / mail_cost
```

Based on independent RFM the number of customers BBB should mail is `r format_nr(nr_mail, dec = 0)` (`r format_nr(perc_mail, perc = TRUE)`). The response rate for the selected customers is predicted to be `r format_nr(rep_rate, perc = TRUE)` or `r format_nr(nr_resp, dec = 0)` buyers. The expected profit is `r format_nr(profit_iq,"$", dec = 0)`. The mailing cost is estimated to be `r format_nr(mail_cost, "$", dec = 0)` with a ROME of `r format_nr(ROME_iq, perc = TRUE)`

## Response rate using sequential quintiles

Create the `mailto_sq` variable for sequential RFM making sure to select the `rfm_sq` variable so the estimates are generated for each cell.

`mailto_sq = mean(buyer == "yes") > .083`

```{r}
## mail TRUE or FALSE
bbb <- group_by(bbb, rfm_sq) %>%
  mutate(mailto_sq = mean(buyer == "yes") > breakeven) %>%
  ungroup()

## also calculate response rate per group as an illustration
bbb <- group_by(bbb, rfm_sq) %>%
  mutate(rfm_sq_resp = mean(buyer == "yes")) %>%
  ungroup()
```

```{r}
result <- pivotr(bbb, cvars = "mailto_sq", fun = "n_obs", normalize = "total")
summary(result, dec = 2, perc = TRUE)
```

```{r}
result <- explore(
  bbb,
  vars = "buyer",
  byvar = "mailto_sq",
  fun = c("n_obs", "mean")
)
summary(result, dec = 4)
```

## Calculate profits and ROME using Sequential RFM

```{r}
perc_mail <- mean(bbb$mailto_sq)
nr_mail <- 500000 * perc_mail
dat <- filter(bbb, mailto_sq == TRUE)
rep_rate <- mean(dat$buyer == "yes")
nr_resp <- nr_mail * rep_rate
mail_cost <- .5 * nr_mail
profit_sq <- (18 - 9 - 3) * nr_resp - mail_cost
ROME_sq <- profit_sq / mail_cost
```

Based on sequential RFM the number of customers BBB should mail is `r format_nr(nr_mail, dec = 0)` (`r format_nr(perc_mail, perc = TRUE)`). The response rate for the selected customers is predicted to be `r format_nr(rep_rate, perc = TRUE)` or `r format_nr(nr_resp, dec = 0)` buyers. The expected profit is `r format_nr(profit_sq,"$", dec = 0)`. The mailing cost is estimated to be `r format_nr(mail_cost, "$", dec = 0)` with a ROME of `r format_nr(ROME_sq, perc = TRUE)`.

Compare this to the main results from independent RFM. The expected profit is `r format_nr(profit_iq,"$", dec = 0)`. The mailing cost is estimated to be `r format_nr(mail_cost, "$", dec = 0)` with a ROME of `r format_nr(ROME_iq, perc = TRUE)`

## Extra: Intuitive groupings

Generate the RFM variables based on intuitive groupings.

```{r}
## create recency groups using case_when
bbb <- mutate(
  bbb,
  rec_ig = case_when(
    last <= 6 ~ 1, 
    last > 6 & last <= 12 ~ 2,
    last > 12 & last <= 18 ~ 3,
    last > 18 & last <= 24 ~ 4, 
    TRUE ~ 5
  )
)

## create frequency groups
bbb <- mutate(bbb, freq_ig = ifelse(purch == 1, 2, 1))

## create monetary groups
bbb <- mutate(bbb, mon_ig = ifelse(total < median(total), 2, 1))

## change all _iq variables to type {integer} using _Data > Transform > Change type_
bbb <- mutate_at(
  bbb,
  .vars = vars(rec_ig, freq_ig, mon_ig),
  .funs = as_integer
)

## create new variable(s)
bbb <- mutate(bbb, rfm_ig = paste0(rec_ig, freq_ig, mon_ig))
```

Create the `mailto_ig` variable for RFM based on intuitive groupings and make sure to select the `rfm_ig` variable so the estimates are generated for each cell.

```{r}
## mail TRUE or FALSE
bbb <- group_by(bbb, rfm_ig) %>%
  mutate(mailto_ig = mean(buyer == "yes") > breakeven) %>%
  ungroup()
```

```{r}
perc_mail <- mean(bbb$mailto_ig)
nr_mail <- 500000 * perc_mail
dat <- filter(bbb, mailto_ig == TRUE)
rep_rate <- mean(dat$buyer == "yes")
nr_resp <- nr_mail * rep_rate
mail_cost <- .5 * nr_mail
profit_ig <- (18 - 9 - 3) * nr_resp - mail_cost
ROME_ig <- profit_ig / mail_cost
```

Based on intuitively grouped RFM the number of customers BBB should mail is `r format_nr(nr_mail, dec = 0)` (`r format_nr(perc_mail, perc = TRUE)`). The response rate for the selected customers is predicted to be `r format_nr(rep_rate, perc = TRUE)` or `r format_nr(nr_resp, dec = 0)` buyers. The expected profit is `r format_nr(profit_ig,"$", dec = 0)`. The mailing cost is estimated to be `r format_nr(mail_cost, "$", dec = 0)` with a ROME of `r format_nr(ROME_ig, perc = TRUE)`.

## Extra: Graphing Profit and ROME across methods

```{r}
## make a tibble (data.frame) with results
dat <- tibble::tibble(
  name = c("No targeting", "Indep. RFM", "Sequen. RFM", "Intuit. RFM"),
  Profit = c(profit_nt, profit_iq, profit_sq, profit_ig),
  ROME = c(ROME_nt, ROME_iq, ROME_sq, ROME_ig)
) %>%
  mutate(name = factor(name, levels = name))
```

```{r fig.width = 5, fig.height = 4}
## plot campaign profit
visualize(
  dat, 
  xvar = "name", 
  yvar = "Profit", 
  type = "bar", 
  labs = list(title = "Campaign profit", x = ""),
  custom = TRUE
) +
  geom_text(aes(label = format_nr(Profit, dec = 0)), vjust = 2)
```

```{r fig.width = 5, fig.height = 4}
## plot ROME
visualize(
  dat, 
  xvar = "name", 
  yvar = "ROME", 
  type = "bar", 
  labs = list(title = "Return on Marketing Expenditures (ROME)", x = ""),
  custom = TRUE
) +
  geom_text(aes(label = format_nr(ROME, dec = 2)), vjust = 2)
```

## Extra: Refining the break even rule with prediction precision based on Independent quintiles

We want to establish that the estimated response rates per RFM cell are significantly larger than the break-even response rate. Lets start with a test of the proportion of buyers in RFM group 111.

```{r fig.width = 7, fig.height = 4.31}
result <- single_prop(
  bbb,
  var = "buyer",
  lev = "yes",
  comp_value = 0.083,
  alternative = "greater",
  data_filter = "rfm_iq == '111'"
)
summary(result)
```

The results show that we can reject $H_0$ in favor of the alternative hypothesis that the proportion of buyers in this group in the population will be above the break-even response rate.

Recall that the "worst" cell we would still target was index 253 for `rfm_iq`. This group had a sample response rate of 0.085. The test below shows that we cannot reject $H_0$ for this group. 

```{r fig.width = 7, fig.height = 4.31}
result <- single_prop(
  bbb,
  var = "buyer",
  lev = "yes",
  comp_value = 0.083,
  alternative = "greater",
  data_filter = "rfm_iq == '253'"
)
summary(result)
```

We can generate the required inputs to calculate the lower-bound on the response rate for each cell using _Data > Explore_ as follows:

```{r}
result <- explore(
  bbb,
  vars = "buyer",
  byvar = "rfm_iq",
  fun = c("n_obs", "prop", "seprop"),
  nr = 95
)
dtab(result, dec = 4) %>% render()
bbb_lbiq <- result$tab
register("bbb_lbiq")
```

Then we can use _Data > Transform_ to calculate the lower-bound on the response rate

```{r}
## create lower-bound
bbb_lbiq <- mutate(bbb_lbiq, prop_lb = prop - 1.64 * seprop)
```

The figure below shows instances where the lower-bound of the confidence interval around the response rate for a cell is below the break-even cut-off point although the sample response rate is above the cut-off point.

```{r fig.width = 10.5, fig.height = 4.67}
visualize(
  bbb_lbiq,
  xvar = "rfm_iq",
  yvar = c("prop", "prop_lb"),
  comby = TRUE,
  type = "line",
  labs = list(
    y = "Proportion of buyer = 'yes'",
    x = "Independent RFM index (rfm_iq)",
    color = ""
  ),
  custom = TRUE
) +
  geom_hline(yintercept = 0.083) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Create the `mailto_lbiq` variable for independent RFM **adjusting for estimation accuracy** making sure to select the `rfm_iq` variable so the estimates are generated for each cell.

    mailto_lbiq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > .083

```{r}
## mail TRUE or FALSE
bbb <- group_by(bbb, rfm_iq) %>%
  mutate(mailto_lbiq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > 0.083) %>%
  ungroup()
```

The rest of the calculations are the same as before.

```{r}
perc_mail <- mean(bbb$mailto_lbiq)
nr_mail <- 500000 * perc_mail
dat <- filter(bbb, mailto_lbiq == TRUE)
rep_rate <- mean(dat$buyer == "yes")
nr_resp <- nr_mail * rep_rate
mail_cost <- .5 * nr_mail
profit_lbiq <- (18 - 9 - 3) * nr_resp - mail_cost
ROME_lbiq <- profit_lbiq / mail_cost
```

Based on independent RFM, after adjustment for prediction precision, the number of customers BBB should mail is `r format_nr(nr_mail, dec = 0)` (`r format_nr(perc_mail, perc = TRUE)`). The response rate for the selected customers is predicted to be `r format_nr(rep_rate, perc = TRUE)` or `r format_nr(nr_resp, dec = 0)` buyers. The expected profit is `r format_nr(profit_lbiq,"$", dec = 0)`. The mailing cost is estimated to be `r format_nr(mail_cost, "$", dec = 0)` with a ROME of `r format_nr(ROME_lbiq, perc = TRUE)`.

## Extra: Refining the break even rule with prediction precision based on Sequential quintiles

We want to establish that the estimated response rates per RFM cell are significantly larger than the break-even response rate. Lets start with a test of the proportion of buyers in RFM group 111.

```{r}
result <- single_prop(
  bbb,
  var = "buyer",
  lev = "yes",
  comp_value = 0.083,
  alternative = "greater",
  data_filter = "rfm_sq == '111'"
)
summary(result)
```

The results show that we can reject $H_0$ in favor of the alternative hypothesis that the proportion of buyers in this group in the population will be above the break-even response rate.

Recall that the "worst" groups we would still send to was index 323 for `rfm_sq`. This group had a sample response rate of 0.085. The test below shows that we cannot reject $H_0$ for this group. 

```{r}
result <- single_prop(
  bbb,
  var = "buyer",
  lev = "yes",
  comp_value = 0.083,
  alternative = "greater",
  data_filter = "rfm_sq == '323'"
)
summary(result)
```

We can generate the required inputs to calculate the lower-bound on the response rate for each cell using _Data > Explore_ as follows:

```{r}
result <- explore(
  bbb,
  vars = "buyer",
  byvar = "rfm_sq",
  fun = c("n_obs", "prop", "seprop"),
  nr = 95
)
dtab(result, dec = 4) %>% render()
bbb_lbsq <- result$tab
register("bbb_lbsq")
```

Then we can use _Data > Transform_ to calculate the lower-bound on the response rate

```{r}
## create lower-bound
bbb_lbsq <- mutate(bbb_lbsq, prop_lb = prop - 1.64 * seprop)
```

The figure below shows instances where the lower-bound of the confidence interval around the response rate for a cell is below the break-even cut-off point although the sample response rate is above the cut-off point.

```{r fig.width = 10.5, fig.height = 4.67}
visualize(
  bbb_lbsq,
  xvar = "rfm_sq",
  yvar = c("prop", "prop_lb"),
  comby = TRUE,
  type = "line",
  labs = list(
    y = "Proportion of buyer = 'yes'",
    x = "Sequential RFM index (rfm_sq)",
    color = ""
  ),
  custom = TRUE
) +
  geom_hline(yintercept = 0.083) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Create the `mailto_lbsq` variable for sequential RFM **adjusting for estimation accuracy** making sure to select the `rfm_sq` variable so the estimates are generated for each cell.

    mailto_lbsq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > .083

```{r}
## mail TRUE or FALSE
bbb <- group_by(bbb, rfm_sq) %>%
  mutate(mailto_lbsq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > 0.083) %>%
  ungroup()
```

The rest of the calculations are the same as before.

```{r}
perc_mail <- mean(bbb$mailto_lbsq)
nr_mail <- 500000 * perc_mail
dat <- filter(bbb, mailto_lbsq == TRUE)
rep_rate <- mean(dat$buyer == "yes")
nr_resp <- nr_mail * rep_rate
mail_cost_lbsq <- .5 * nr_mail
profit_lbsq <- (18 - 9 - 3) * nr_resp - mail_cost_lbsq
ROME_lbsq <- profit_lbsq / mail_cost_lbsq
```

Based on sequential RFM, after adjustment for prediction precision, the number of customers BBB should mail is `r format_nr(nr_mail, dec = 0)` (`r format_nr(perc_mail, perc = TRUE)`). The response rate for the selected customers is predicted to be `r format_nr(rep_rate, perc = TRUE)` or `r format_nr(nr_resp, dec = 0)` buyers. The expected profit is `r format_nr(profit_lbsq,"$", dec = 0)`. The mailing cost is estimated to be `r format_nr(mail_cost_lbsq, "$", dec = 0)` with a ROME of `r format_nr(ROME_lbsq, perc = TRUE)`.


Updating profit and ROME plots:

```{r}
## make a tibble (data.frame) with results
bbb_results <- tibble::tibble(
  name = c("No targeting", "Indep. RFM", "Sequen. RFM", "Intuit. RFM", "Indep. lb RFM", "Seq. lb RFM"),
  Profit = c(profit_nt, profit_iq, profit_sq, profit_ig, profit_lbiq, profit_lbsq),
  ROME = c(ROME_nt, ROME_iq, ROME_sq, ROME_ig, ROME_lbiq, ROME_lbsq)
) %>%
  mutate(name = factor(name, levels = name))
register("bbb_results")
```

```{r fig.width = 6, fig.height = 4}
## plot campaign profit
visualize(
  bbb_results,
  xvar = "name",
  yvar = "Profit",
  type = "bar",
  labs = list(title = "Campaign profit", x = ""),
  custom = TRUE
) +
  geom_text(aes(label = format_nr(Profit, dec = 0)), vjust = 2)
```

```{r fig.width = 6, fig.height = 4}
## plot ROME
visualize(
  bbb_results,
  xvar = "name",
  yvar = "ROME",
  type = "bar",
  labs = list(title = "Return on Marketing Expenditures (ROME)", x = ""),
  custom = TRUE
) +
  geom_text(aes(label = format_nr(ROME, dec = 2)), vjust = 2)
```
 

